6.867 Problem Set 1

### 2015-12-10 Project/Latex/Paper.tex

Despite the fact that our training isn't finished, both our neural network-based language models are already performing better than a standard bi-gram model with smoothing. We build 2 sets of article perplexity scores. One set is derived from the smoothed bigram model to serve as a base comparison. Our other set is derived from the most recently completed pass of our trigram NN language model. We report the following article perplexity scores distribution:

@@

Its important to note however, that we don't necessarily care exactly how good our language model. Since we only use the language model as an intermediate step to construct a feature for a regression task. It could very well be the case features generated by a worse language model can work just as well as well in the regression task as features generated by a better language model if the relative variation of articles is maintained. To test whether a better language model can give us more predictive power, we compute two sets of perplexity scores, one based on the smoothed bigram language model and one based on the current best trigram neural network language model.

>>>>

Despite the fact that our training isn't finished, both our neural network-based language models have already achieved lower negative average log-likelihood compared to the smoothed standard bi-gram model. We build 2 sets of article perplexity scores. One set is derived from the smoothed bigram model to serve as a base comparison. Our other set is derived from the most recently completed pass of our trigram NN language model. We report the following article perplexity scores distribution:

@@

Its important to note however, that we only care about the goodness of the underlying language model insofar that a better language will produce features with better predictive power. However, it could very well be the case features generated by a worse language model can work just as well as well as features generated by a better language model in the regression model if the relative variation of articles is maintained. Hence our reasoning to produce the two sets of perplexity scores.
